Social Attention for Autonomous Decision-Making in Dense Traffic

### 2019-09-11 main.tex
Updates from Overleaf

This observation has led the community to turn to learning-based methods, which bear the promise of leveraging data to automatically learn a complex driving policy. In the imitation learning approach, a policy can be trained in a supervised manner to imitate human driving decisions \citep[e.g.][]{Pomerleau1989, Ross2011, Bojarski2016, Xu2016, Eraqi2017, Codevilla2017, Rehder2017c, Rezagholiradeh2018, Rhinehart2018, Bansal2018, Rhinehart2019}. Because the cost of human driving data collection at large scale can be prohibitive, another promising approach is train a policy in simulation using reinforcement learning \citep[e.g.][]{Cardamone2009, Ross2011, Mukadam2017, Chen2017, Isele2017, Isele2018, Ha2018, Kendall2019}.

@@

\paragraph{State-representation for social interactions}{

>>>>

This observation has led the community to turn to learning-based methods, which bear the promise of leveraging data to automatically learn a complex driving policy. In the imitation learning approach, a policy can be trained in a supervised manner to imitate human driving decisions \citep[e.g.][]{Pomerleau1989, Ross2011, Bojarski2016, Xu2016, Eraqi2017, Codevilla2017, Rehder2017c, Rezagholiradeh2018, Rhinehart2018, Bansal2018, Rhinehart2019}. Because the cost of human driving data collection at large scale can be prohibitive, another promising approach is train a policy in simulation using reinforcement learning \citep[e.g.][]{Cardamone2009, Ross2011, Mukadam2017, Chen2017, Isele2018, Ha2018, Kendall2019}.

@@

\paragraph{State-representation for social interactions}
